Factors affecting reliablity of state-space age-structured assessment models

### 2023-02-10 Project_0/paper/paper.Rmd
working on Ecov-M sims

---
title: How reliable are inferences from state-space age-structured assessment models?
author: 
  - Timothy J. Miller^1^, Britten, Brooks, Fay, Legault, Stock, 
date: ''
fontsize: 12pt
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    includes:
      in_header:
      - options.sty
      - journalshortcuts.tex
    keep_tex: yes
    number_sections: yes
  html_document:
    df_print: paged
  word_document: default
header-includes:
- \usepackage{xspace}
- \usepackage{bm}
- \usepackage{caption,graphics}
- \usepackage{graphicx}
- \usepackage{makecell}
- \renewcommand\figurename{Fig.}
- \captionsetup{labelsep=period, singlelinecheck=false}
- \newcommand{\changesize}[1]{\fontsize{#1pt}{#1pt}\selectfont}
- \renewcommand{\arraystretch}{1.5}
- \renewcommand\theadfont{}
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
biblio-style: cjfas2.bst
---

@@

@@

Used the WHAM package  \citep[][commit 77bbd94]{stockmiller21} (Miller and Stock 2020). This packages has also been used to configure operating and estimating models for closed loop simulations evaluating index-based assessment methods \citep{legaultetalinpress}.

>>>>

---
title: Factors affecting reliablity of state-space age-structured assessment models
author: 
  - Timothy J. Miller^1^, Britten, Brooks, Fay, Legault, Stock, et al.
date: ''
fontsize: 12pt
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    includes:
      in_header:
      - options.sty
      - journalshortcuts.tex
    keep_tex: yes
    number_sections: yes
  html_document:
    df_print: paged
  word_document: default
header-includes:
- \usepackage{xspace}
- \usepackage{bm}
- \usepackage{caption,graphics}
- \usepackage{graphicx}
- \usepackage{makecell}
- \renewcommand\figurename{Fig.}
- \captionsetup{labelsep=period, singlelinecheck=false}
- \newcommand{\changesize}[1]{\fontsize{#1pt}{#1pt}\selectfont}
- \renewcommand{\arraystretch}{1.5}
- \renewcommand\theadfont{}
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
biblio-style: cjfas2.bst
---

@@

Here we conduct a simulation study with operating models varying by degree of observation error uncertainty, sources of process error (M, NAA, q, sel), and fishing history. The simulations from these operating models are fitted with estimating models that make alternative assumptions for sources of process error (M, NAA< q, sel), whether a stock-recruit model was estimated, and whether M is estimated. We evaluate whether AIC can correctly determine the correct source of process error and stock effects on recruitment. We also evaluate the degree of bias in the outputs of the assessment model that are important for management.

@@

Used the WHAM package  \citep[][commit 77bbd94]{stockmiller21} (Miller and Stock 2020). This packages has also been used to configure operating and estimating models for closed loop simulations evaluating index-based assessment methods \citep{legaultetalinpress} and is used for management of haddock, butterfish, plaice, bluefish in the Northeast US.
